### 2024-04-18 docs/SOSP 2024/motivation.tex
Minor edit to motivation
Put sensitivity figures next to each other

Consider a model with four trees, two 
trees of depth 1 and two of depth 2 (Figure \ref{Fig:HIRExample}).
% We use this model as our running example throughout this section.
We first describe a simple schedule that processes one tree at a time 
for all input rows. The scheduling constructs are fairly intuitive. We 
defer a detailed explanation of the scheduling language to Section~\ref{sec:scheduling}. 
The loop over the trees is split into two -- one that
iterates over the first two trees (Trees 1 and 2 with depth 1) and 
the second that iterates over the last two trees (Trees 3 and 4 with
depth 2). Straightforward traversal of trees involves branching. 
One way to avoid this as done in this schedule is to unroll the 
tree walks for each tree. 
When the schedule specifies that the tree walks should be unrolled, 
\Treebeard{} pads the trees so that all leaves are at the same depth.

@@

\begin{figure}[]
  \centering
  \begin{subfigure}[b]{.3\textwidth}
    \subcaptionbox*{}{\includegraphics[width=\textwidth]{figures/batch_sensitivity_covtype.png}}
    \caption{\label{fig:sensitivitya} Batch sensitivity for \op{covtype}. Each point shows the slowdown when best schedule for the 
    x-axis batch size is used for the y-axis batch size.}
  \end{subfigure}
  % \hfill  % Add horizontal space between subfigures
  \begin{subfigure}[b]{.3\textwidth}
    \subcaptionbox*{}{\includegraphics[width=\textwidth]{figures/model_sensitivity_4096.png}}
    \caption{\label{fig:sensitivityb} Model sensitivity for batch size 4096. Each point shows the slowdown when best schedule for the
    x-axis model is used for the y-axis model.}
  \end{subfigure}
\end{figure}

>>>>

Consider a model with four trees, two 
trees of depth 1 and two of depth 2 (Figure \ref{Fig:HIRExample}).
% We use this model as our running example throughout this section.
We first describe a simple schedule that processes one tree at a time 
for all input rows. The scheduling constructs are fairly intuitive. We 
defer a detailed explanation of the scheduling language to Section~\ref{sec:scheduling}. 
The loop over the trees is split into two -- one that
iterates over the first two trees (Trees 1 and 2 with depth 1) and 
the second that iterates over the last two trees (Trees 3 and 4 with
depth 2). Straightforward traversal of trees requires a \op{while} loop
and involves branching to check if a leaf has been reached. 
One way to avoid this as done in this schedule is to unroll the 
tree walks for each tree. 
When the schedule specifies that the tree walks should be unrolled, 
\Treebeard{} pads the trees so that all leaves are at the same depth.

@@

\begin{figure}[htb]
  \begin{subfigure}[t]{.45\linewidth}
    \centering
    \includegraphics[width=\linewidth]{figures/batch_sensitivity_covtype.png}
    \caption{\label{fig:sensitivitya}\op{covtype} batch sensitivity}
  \end{subfigure}
  \begin{subfigure}[t]{.45\linewidth}
    \centering
    \includegraphics[width=\linewidth]{figures/model_sensitivity_4096.png}
    \caption{\label{fig:sensitivityb}Model sensitivity at batch size 4096}
\end{subfigure}
  \caption{Batch and model sensitivity plots. Each point shows the slowdown when best schedule for the
          x-axis batch size (model) is used for the y-axis batch size (model).}
\end{figure}

% \begin{figure}[htb]
%   \begin{minipage}[t]{.475\linewidth}
%     \subcaptionbox*{}{\includegraphics[width=\linewidth]{figures/batch_sensitivity_covtype.png}}
%     \caption{\label{fig:sensitivitya}Batch sensitivity for \op{covtype}}
%   \end{minipage}
%   \begin{minipage}[t]{.475\linewidth}
%     \subcaptionbox*{}{\includegraphics[width=\linewidth]{figures/model_sensitivity_4096.png}}
%     \caption{\label{fig:sensitivityb}Model sensitivity at batch size 4096}
%   \end{minipage}
%   \caption{Batch and model sensitivity plots. Each point shows the slowdown when best schedule for the
%           x-axis batch size (model) is used for the y-axis batch size (model).}
% \end{figure}
